01-Travel-time-calculation

### 2023-07-30 TRB-manuscript/data-prep/01-Travel-time-calculation.Rmd
TRB draft - ready for AP edits

@@

>>>>

/data-prep/data-raw/intermed/ttresults/output_OD_bike.Rdata
/data-prep/data-raw/intermed/ttresults/output_OD_car.Rdata
/data-prep/data-raw/intermed/ttresults/output_OD_transit.Rdata
/data-prep/data-raw/intermed/ttresults/output_OD_walk.Rdata

@@

Resave but with ZT1259 codes:
```{r}
load("data-prep/data/zn1259.RData") 
zn1259 <- zn %>% dplyr::select(c("FID", "CD_ZT12", "ZT1259"))
remove(zn)

#associate the ZT11259 ids to the calculated travel times. 
list_ZT1259_FID <- zn1259 %>% dplyr::select(c("ZT1259", "FID")) %>% st_drop_geometry()

calc_bikett <- list_ZT1259_FID %>% 
  merge(output_OD_bike, by.x = "FID", by.y="fromId") %>% 
  rename("VORIZT1259" = "ZT1259") %>% dplyr::select(-FID) %>%
  merge(list_ZT1259_FID, by.y = "FID", by.x="toId") %>% 
  rename("VDESZT1259" = "ZT1259") %>% transmute(VORIZT1259, VDESZT1259, travel_time)
rm("output_OD_bike")

calc_walktt <- list_ZT1259_FID %>% 
  merge(output_OD_walk, by.x = "FID", by.y="fromId") %>% 
  rename("VORIZT1259" = "ZT1259") %>% dplyr::select(-FID) %>%
  merge(list_ZT1259_FID, by.y = "FID", by.x="toId") %>% 
  rename("VDESZT1259" = "ZT1259") %>% transmute(VORIZT1259, VDESZT1259, travel_time)
rm("output_OD_walk")

calc_transittt <- list_ZT1259_FID %>% 
  merge(output_OD_transit, by.x = "FID", by.y="fromId") %>% 
  rename("VORIZT1259" = "ZT1259") %>% dplyr::select(-FID) %>%
  merge(list_ZT1259_FID, by.y = "FID", by.x="toId") %>% 
  rename("VDESZT1259" = "ZT1259") %>% transmute(VORIZT1259, VDESZT1259, travel_time)
rm("output_OD_transit")

calc_cartt <- list_ZT1259_FID %>% 
  merge(output_OD_car, by.x = "FID", by.y="fromId") %>% 
  rename("VORIZT1259" = "ZT1259") %>% dplyr::select(-FID) %>%
  merge(list_ZT1259_FID, by.y = "FID", by.x="toId") %>% 
  rename("VDESZT1259" = "ZT1259") %>% transmute(VORIZT1259, VDESZT1259, travel_time)
rm("output_OD_car")

save("calc_bikett", file = "data-raw/intermed/ttresults/calc_bikett.Rdata")
save("calc_walktt", file = "data-raw/intermed/ttresults/calc_walktt.Rdata")
save("calc_transittt", file = "data-raw/intermed/ttresults/calc_transittt.Rdata")
save("calc_cartt", file = "data-raw/intermed/ttresults/calc_cartt.Rdata")
```
